### 2017-02-27 2017mergingmerges/section/XX-Evaluation.tex
update graph with +merge and -merge counts

\begin{minipage}[t]{0.4\textwidth}
\begin{tikzpicture}
\begin{axis}[
	ylabel=Process states,
	xlabel=Split combinators,
  ymin=0, ymax=100,
	enlargelimits=0.01,
	ybar interval=0.7,
  width=7.5cm, height=6.5cm,
]
\addplot coordinates {(1,9) (2,9) (3,14) (4,19) (5,24) (6,29) (7,34)
  % Last one doesn't show for some reason, so add one above the max 
    (8,100) };
\end{axis}
\end{tikzpicture}
\end{minipage}
\begin{minipage}[t]{0.10\textwidth}
\quad
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{tikzpicture}
\begin{axis}[
%	ylabel=Process states,
	xlabel=Pipelined combinators,
  ymin=0, ymax=100,
	enlargelimits=0.01,
	ybar interval=0.7,
  width=7.5cm, height=6.5cm,
]
\addplot coordinates {(1,9) (2,17) (3,27) (4,37) (5,47) (6,57) (7,67)
  % Last one doesn't show for some reason, so add one above the max 
  (8,100) };
\end{axis}
\end{tikzpicture}
\end{minipage}

\caption{Maximum number of process states for all combinations of up to $n$ combinators.}
\label{fig:bench:other}
\end{figure}

>>>>

\begin{minipage}[t]{0.4\textwidth}
\begin{tikzpicture}
\begin{axis}[
	ylabel=Process states,
	xlabel=Split combinators,
  ymin=0, ymax=100,
	enlargelimits=0.01,
	ybar interval=0.7,
  width=7.5cm, height=6.5cm,
	legend pos=north west,
	%legend style={at={(0.01,0.99)},anchor=north west},
]
\addplot coordinates {(1,9) (2,27) (3,40) (4,53) (5,66) (6,79) (7,92)
  % Last one doesn't show for some reason, so add one above the max 
    (8,100) };

\addplot coordinates {(1,4) (2,9) (3,14) (4,19) (5,24) (6,29) (7,34)
  % Last one doesn't show for some reason, so add one above the max 
    (8,100) };

\legend{All combinators, Without merge};

\end{axis}
\end{tikzpicture}
\end{minipage}
\begin{minipage}[t]{0.10\textwidth}
\quad
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{tikzpicture}
\begin{axis}[
%	ylabel=Process states,
	xlabel=Pipelined combinators,
  ymin=0, ymax=100,
	enlargelimits=0.01,
	ybar interval=0.7,
  width=7.5cm, height=6.5cm,
	legend pos=north west,
]
\addplot coordinates {(1,9) (2,17) (3,27) (4,37) (5,47) (6,57) (7,67)
  % Last one doesn't show for some reason, so add one above the max 
  (8,100) };

\addplot coordinates {(1,4) (2,9) (3,14) (4,19) (5,24) (6,29) (7,34)
  % Last one doesn't show for some reason, so add one above the max 
    (8,100) };

\legend{All combinators, Without merge};

\end{axis}
\end{tikzpicture}
\end{minipage}

\caption{Maximum output process size for fusing all combinations of up to $n$ combinators.}
\label{fig:bench:other}
\end{figure}
